Wait-free Queues with Polygarithmic Step Complexity

### 2022-08-18 article/psuedocode.tex
new notation for E(n,b,i)

\Function{<int, int>}{FindResponse}{\sl{int} b, \sl{int} i}\Statex\cmt{Returns the the response to the $D_{root,b,i}$.}
\If{\tt{ root.blocks[b-1].\size}\tt{ + root.blocks[b].num\sub{enq} - i $<$ 0}} \State \Return \tt{null} \label{checkEmpty}\cmt{Check if the queue is empty.}
\Else
\State \tt{e= i - root.blocks[b-1].size + root.blocks[b-1].sum\sub{enq}} \label{computeE}
\Statex\cmt{$E_{root,e}$ is the response.}
\State \Return \tt{root.GetENQ(root.\Call{DSearch}{e, b})}\label{findAnswer}
\EndIf
\EndFunction{FindResponse}

@@

\end{multicols}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}
\caption{Root}
\begin{algorithmic}[1]
\setcounter{ALG@line}{800}
\Statex
\Statex $\leadsto$ \textsf{Precondition: \tt{root.blocks[end].sum\sub{enq} $\geq$ \tt{e}}}
\Function{<int, int>}{DSearch}{\sl{int} e, \sl{int} end}
\cmt{Returns \tt{<b,i>} if $E_{root,e}=E_{root,b,i}$.}
\State \tt{start= end-1}
\While{\tt{root.blocks[start].sum\sub{enq}}$\geq$\tt{e}}
\State \tt{start= max(start-(end-start), 0)} \label{doubling}
\EndWhile
\State \tt{b= root.BSearch(sum\sub{enq}, e, start, end)}
\State \tt{i= e- root.blocks[b-1].sum\sub{enq}} \label{DSearchComputei}
\State\Return \tt{<b,i>}
\EndFunction{DSearch}
\end{algorithmic}
\end{algorithm}

@@

\Statex $\leadsto$ \textsf{Precondition:~\tt{blocks[b].num\sub{enq}$\geq$i$\geq 1$}}
\Function{element}{GetEnq}{\sl{int} b, \sl{int} i} \cmt{Returns the element of $E_{this,b,i}$.}
\If{\tt{this} \bf{is} \tt{leaf}}
\State\Return \tt{blocks[b].element} \label{getBaseCase}
\ElsIf{\tt{i $\leq$ blocks[b].num\sub{enq-left}}} \label{leftOrRight} \cmt{$E_{this,b,i}$ is in the left child of this node.}
\State \tt{subBlock= left.\Call{BSearch}{sum\sub{enq}, i+blocks[b-1].sum\sub{enq-left}, blocks[b-1].end\sub{left}+1, blocks[b].end\sub{left}}} \label{leftChildGet}
\State \Return\tt{left.}\Call{GetEnq}{subBlock, i} 
\Else
\State \tt{i= i-blocks[b].num\sub{enq-left}}
\State\tt{subBlock= right.\Call{BSearch}{sum\sub{enq}, i+right.blocks[b-1].sum\sub{enq-right}, blocks[b-1].end\sub{right}+1, blocks[b].end\sub{right}}} \label{rightChildGet}
\State \Return\tt{right.}\Call{GetEnq}{subBlock, i} 
\EndIf
\EndFunction{GetEnq}

@@

\begin{itemize}
\item The prefix of an operation $op$ in the sequence of operations $S$ is the sequence of operations strictly before $op$.
  \item $E(n,b)$ is the sequence of enqueue operations in \nf{ops(n.blocks[b])} defined recursively as follows. $E(leaf,b)$ is the single enqueue operation in \nf{ops(leaf.blocks[b])} or an empty sequence if \nf{leaf.blocks[b].num\sub{enq}=0}. If \nf{n} is an internal node, then
\begin{align*} 
E(n,b) =&  E(n.left,n.blocks[b-1].end\sub{left}+1)\cdot E(n.left,n.blocks[b-1].end\sub{left}+2)\cdots E(n.left,n.blocks[b].end\sub{left})\cdot \\ 
&E(n.right,n.blocks[b-1].end\sub{right}+1)\cdot E(n.right,n.blocks[b-1].end\sub{right}+2)\cdots E(n.right,n.blocks[b].end\sub{right})
\end{align*}
  \item $E_{n,b,i}$ is the $i$th enqueue in $E(n,b)$.
\item The order of the enqueue operations in the node $n$ is $E(n)=E(n,1)\cdot E(n,2)\cdot E(n,3)\cdots$
\item $E_{n,i}$ is the $i$th enqueue in $E(n)$.
  \item $D(n,b)$ is the sequence of dequeue operations in \nf{ops(n.blocks[b])} defined recursively as follows. $D(leaf,b)$ is the single dequeue operation in \nf{ops(leaf.blocks[b])} or an empty sequence if \nf{leaf.blocks[b].num\sub{deq}=0}. If \nf{n} is an internal node, then
\begin{align*} 
D(n,b) =&  D(n.left,n.blocks[b-1].end\sub{left}+1)\cdot D(n.left,n.blocks[b-1].end\sub{left}+2)\cdots D(n.left,n.blocks[b].end\sub{left})\cdot \\ 
&D(n.right,n.blocks[b-1].end\sub{right}+1)\cdot D(n.right,n.blocks[b-1].end\sub{right}+2)\cdots D(n.right,n.blocks[b].end\sub{right})
\end{align*}
    \item $D_{n,b,i}$ is the $i$th enqueue in $D(n,b)$.
\item The order of the dequeue operations in the node $n$: $D(n)=D(n,1)\cdot D(n,2)\cdot D(n,3)...$
\item $D_{n,i}$ is the $i$th dequeue in $D(n)$.
\end{itemize}
\end{definition}

@@

\begin{lemma}[Get correctness] \label{get}
If \nf{n.blocks[b].num\sub{enq}$\geq$i} then \nf{n.GetENQ(b,i)} returns the \nf{element} enqueued by $E_{n,b,i}$.
\end{lemma}
\begin{proof}
We are going to prove this lemma by induction on the height of node \nf{n}. For the base case \nf{n} is a leaf. Leaf blocks each contain exactly one operation, so by the preconditions of \nf{GetENQ()}, only \nf{n.GetENQ(b,1)} can be called and \nf{n.blocks[b]} contains an enqueue. At Line \ref{getBaseCase} \nf{n.GetENQ(b,1)} returns the \nf{element} of the \nf{enqueue} operation stored in the $b$th block of leaf \nf{n} .

For the induction step we prove \nf{n.GetENQ(b,i)} returns $E_{n,b,i}$, if \nf{n.child.GetENQ(b,i)} returns $E_{n.child,b,i}$. In  Line \ref{leftOrRight} it is decided for the non-leaf nodes that the \nf{i}th enqueue in  \nf{b}th block  of internal node \nf{n} is in the \nf{n.blocks[b]}'s left child or right child subblocks. From Definition  \ref{ordering} of $E(n,b)$ we know enqueue operations in a block are ordered by their process id and since the leaves of the tree are ordered by process id from left to right, thus operations from the left subblocks come before operations from the right subblocks in a block (See Figure \ref{figGet}). Furthermore the \nf{num\sub{enq-left}} field  in a block stores the number of \nf{enqueue()} operations from the blocks's subblocks in the left child of \nf{n}. So $i$th enqueue operation is propagated from the right child if \nf{i} is greater than \nf{b.num\sub{enq-left}}. otherwise we should search for the $i$th enqueue in the left child. By definition \ref{def::ops} and \ref{def::subblock} we need to search in subblocks of \nf{n.blocks[b]} from the range \texttt{n.left.blocks[n.blocks[i-1].end\textsubscript{left}+1..n.blocks[i].end\textsubscript{left}]} $\cup$ \texttt{n.right.blocks[n.blocks[i-1].end\textsubscript{right}+1..n.blocks[i].end\textsubscript{right}]}.

If the $i$th \nf{enqueue} of \nf{n.blocks[b]} is in the left child it would be $i$th enqueue in \texttt{n.left.blocks[n.blocks[i-1].end\textsubscript{left}+1..n.blocks[i].end\textsubscript{left}]} by Definition \ref{def::subblock}. Also we know there are $eb=n.blocks[b-1].sum_{enq-left}$ enqueues in the blocks before this range, so $E_{n,b,i}$ is $E_{n.left, i+eb}$ which is $E_{n.left,b^\prime,i^\prime}$ for some $b^\prime$ and $i^\prime$. We can compute $b^\prime$ search for $i+eb$th enqueue in \tt{n.left} and $i^\prime$ is \tt{i+eb-n.left.blocks[}$b^\prime-1$\tt{].sum\sub{enq}}. The parameters in \ref{leftChildGet} are for searching $E_{n.left, i+eb}$ in \nf{n.left.block} in the expected range of blocks, so this \nf{BSearch} returns the index of the subblock containing $E_{n,b,i}$.

Else if the enqueue we are looking for is in the right child then there are \nf{n.blocks[b].num\sub{enq-left}} enqueues ahead of it in \nf{n.blocks[b]} but not in \texttt{n.right.blocks[n.blocks[i-1].end\textsubscript{right}+1..n.blocks[i].end\textsubscript{right}]}. So we need to search for \nf{i-n.blocks[b].num\sub{enq-left}+ n.blocks[b-1].sum\sub{enq-right}} (Line \ref{rightChildGet}). Other parameters are assigned similar for the left child. So in both cases the direct subblock containing $E_{n,b,i}$ is computed in Lines \ref{leftChildGet} and \ref{rightChildGet}.

 Finally, \nf{n.child.GetENQ()} is invoked on the subblock containing $E_{n,b,i}$ which returns $E_{n,b,i}$ by the hypothesis of the induction.
\end{proof}

@@

\begin{lemma}[DSearch correctness] \label{dsearch}
Assume \nf{root.blocks[end].sum\sub{enq}}$\geq$\nf{e} and $E_{root, e}$'s \nf{element} is the response to some \nf{Dequeue()} operation in \nf{root.blocks[end]}.  \nf{DSearch(e, end)} returns \nf{<b, i>} such that $E_{root,b,i}= E_{root,e}$.
\end{lemma}
\begin{proof}
It is trivial to see that the doubling search from \nf{root.blocks[end]} to \nf{root.blocks[0]} will find $E_{root,e}$ eventually. Because \nf{root.blocks[].sum\sub{enq}} is an increasing value from 0 to some value greater than \nf{e}. So there is a \nf{b} that \nf{root.blocks[b].sum\sub{enq}}$>e$ but \nf{root.blocks[b-1].sum\sub{enq}}$<e$.

@@

Hello Im hoseen master student in cs at York uni. I will defend my thesis by Nov this year and I was looking for ful time jobs starting from novomber. I have experince in both acdemia and indusrty. When I was a bachelors srudent I workd from 2 years as a Software dveloper. I have expereince with backend devlopment. I have implemented, deploeyd an maintained backend systems.

@@

\begin{lemma}[Computing Response] \label{computeHead}
\nf{FindResponse(b,i)} returns \nf{R(D\sub{root,b,i}).element}.
\end{lemma}
\begin{proof}
First note that by Definition \ref{ordering} the linearization ordering  of operations will not change as new operations come so instead of talking about the linearization of operations before the $E_{root, b, i}$ we talk about what if the whole operation in the linearization are applied on a queue.

$D_{root,b,i}$ is $D_{root,root.blocks[b-1].sum_{deq}+i}$ from the definition \ref{ordering} and \it{$sum_{enq}$}.  $D_{root,b,i}$ returns \nf{null} if \nf{root.blocks[b-1].\size+ root.blocks[b].num\sub{enq}- i <0} by Lemma \ref{nullReturn} (Line \ref{checkEmpty}). Otherwise if it is $d^\prime$th non-null dequeue in $L$ it returns $d^\prime$th enqueue by Observation \ref{responseToADeq} . By Lemma \ref{numberOfNND} there are \nf{root.blocks[b-1].sum\sub{enq} - root.blocks[b-1].\size} non-null dequeue operations before prefix for \nf{root.blocks[b-1]}. Note that the dequeues in \nf{root.blocks[b]} before the $i$th dequeue are non-null dequeues. So the response is $E_{root,i - root.blocks[b-1].size + root.blocks[b-1].sum\sub{deq}}$ (Line \ref{computeE}). See figure \ref{computeResponseDetail}.

After computing \nf{e} we can find \nf{b,i} such that $E_{root,b,i}=E_{root,e}$ using \nf{DSearch} and then find its \nf{element} using \nf{GetEnq} (Line \ref{findAnswer}).
\end{proof}

\begin{figure}[hbt]  
  \center\includegraphics[width=2in]{pics/computeResponseDetail.png}\caption{The position of $E_{root,b,i}$.}
\label{computeResponseDetail}
\end{figure}

>>>>

\Function{<int, int>}{FindResponse}{\sl{int} b, \sl{int} i}\Statex\cmt{Returns the the response to the $D_{root,b,i}$.}
\If{\tt{ root.blocks[b-1].\size}\tt{ + root.blocks[b].num\sub{enq} - i $<$ 0}} \State \Return \tt{null} \label{checkEmpty}\cmt{Check if the queue is empty.}
\Else
\State \tt{e= i - root.blocks[b-1].size + root.blocks[b-1].sum\sub{enq}} \label{computeE}
\Statex\cmt{$E_e(root)$ is the response.}
\State \Return \tt{root.GetENQ(root.\Call{DSearch}{e, b})}\label{findAnswer}
\EndIf
\EndFunction{FindResponse}

@@

\end{multicols}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}
\caption{Root}
\begin{algorithmic}[1]
\setcounter{ALG@line}{800}
\Statex
\Statex $\leadsto$ \textsf{Precondition: \tt{root.blocks[end].sum\sub{enq} $\geq$ \tt{e}}}
\Function{<int, int>}{DSearch}{\sl{int} e, \sl{int} end}
\cmt{Returns \tt{<b,i>} if $E_e(root)=E_i(root,b)$.}
\State \tt{start= end-1}
\While{\tt{root.blocks[start].sum\sub{enq}}$\geq$\tt{e}}
\State \tt{start= max(start-(end-start), 0)} \label{doubling}
\EndWhile
\State \tt{b= root.BSearch(sum\sub{enq}, e, start, end)}
\State \tt{i= e- root.blocks[b-1].sum\sub{enq}} \label{DSearchComputei}
\State\Return \tt{<b,i>}
\EndFunction{DSearch}
\end{algorithmic}
\end{algorithm}

@@

\Statex $\leadsto$ \textsf{Precondition:~\tt{blocks[b].num\sub{enq}$\geq$i$\geq 1$}}
\Function{element}{GetEnq}{\sl{int} b, \sl{int} i} \cmt{Returns the element of $E_i(this,b)$.}
\If{\tt{this} \bf{is} \tt{leaf}}
\State\Return \tt{blocks[b].element} \label{getBaseCase}
\ElsIf{\tt{i $\leq$ blocks[b].num\sub{enq-left}}} \label{leftOrRight} \cmt{$E_i(this,b)$ is in the left child of this node.}
\State \tt{subBlock= left.\Call{BSearch}{sum\sub{enq}, i+blocks[b-1].sum\sub{enq-left}, blocks[b-1].end\sub{left}+1, blocks[b].end\sub{left}}} \label{leftChildGet}
\State \Return\tt{left.}\Call{GetEnq}{subBlock, i} 
\Else
\State \tt{i= i-blocks[b].num\sub{enq-left}}
\State\tt{subBlock= right.\Call{BSearch}{sum\sub{enq}, i+right.blocks[b-1].sum\sub{enq-right}, blocks[b-1].end\sub{right}+1, blocks[b].end\sub{right}}} \label{rightChildGet}
\State \Return\tt{right.}\Call{GetEnq}{subBlock, i} 
\EndIf
\EndFunction{GetEnq}

@@

\begin{itemize}
\item The prefix of an operation $op$ in the sequence of operations $S$ is the sequence of operations strictly before $op$.
  \item $E(n,b)$ is the sequence of enqueue operations in \nf{ops(n.blocks[b])} defined recursively as follows. $E(leaf,b)$ is the single enqueue operation in \nf{ops(leaf.blocks[b])} or an empty sequence if \nf{leaf.blocks[b].num\sub{enq}=0}. If \nf{n} is an internal node, then
\begin{align*} 
E(n,b) =&  E(n.left,n.blocks[b-1].end\sub{left}+1)\cdot E(n.left,n.blocks[b-1].end\sub{left}+2)\cdots E(n.left,n.blocks[b].end\sub{left})\cdot \\ 
&E(n.right,n.blocks[b-1].end\sub{right}+1)\cdot E(n.right,n.blocks[b-1].end\sub{right}+2)\cdots E(n.right,n.blocks[b].end\sub{right})
\end{align*}
  \item $E_i(n,b)$ is the $i$th enqueue in $E(n,b)$.
\item The order of the enqueue operations in the node $n$ is $E(n)=E(n,1)\cdot E(n,2)\cdot E(n,3)\cdots$
\item $E_i(n)$ is the $i$th enqueue in $E(n)$.
  \item $D(n,b)$ is the sequence of dequeue operations in \nf{ops(n.blocks[b])} defined recursively as follows. $D(leaf,b)$ is the single dequeue operation in \nf{ops(leaf.blocks[b])} or an empty sequence if \nf{leaf.blocks[b].num\sub{deq}=0}. If \nf{n} is an internal node, then
\begin{align*} 
D(n,b) =&  D(n.left,n.blocks[b-1].end\sub{left}+1)\cdot D(n.left,n.blocks[b-1].end\sub{left}+2)\cdots D(n.left,n.blocks[b].end\sub{left})\cdot \\ 
&D(n.right,n.blocks[b-1].end\sub{right}+1)\cdot D(n.right,n.blocks[b-1].end\sub{right}+2)\cdots D(n.right,n.blocks[b].end\sub{right})
\end{align*}
    \item $D_i(n,b)$ is the $i$th enqueue in $D(n,b)$.
\item The order of the dequeue operations in the node $n$: $D(n)=D(n,1)\cdot D(n,2)\cdot D(n,3)...$
\item $D_i(n)$ is the $i$th dequeue in $D(n)$.
\end{itemize}
\end{definition}

@@

\begin{lemma}[Get correctness] \label{get}
If \nf{n.blocks[b].num\sub{enq}$\geq$i} then \nf{n.GetENQ(b,i)} returns the \nf{element} enqueued by $E_i(n,b)$.
\end{lemma}
\begin{proof}
We are going to prove this lemma by induction on the height of node \nf{n}. For the base case \nf{n} is a leaf. Leaf blocks each contain exactly one operation, so by the preconditions of \nf{GetENQ()}, only \nf{n.GetENQ(b,1)} can be called and \nf{n.blocks[b]} contains an enqueue. At Line \ref{getBaseCase} \nf{n.GetENQ(b,1)} returns the \nf{element} of the \nf{enqueue} operation stored in the $b$th block of leaf \nf{n} .

For the induction step we prove \nf{n.GetENQ(b,i)} returns $E_i(n,b)$, if \nf{n.child.GetENQ(b,i)} returns $E_i(n.child,b)$. In  Line \ref{leftOrRight} it is decided for the non-leaf nodes that the \nf{i}th enqueue in  \nf{b}th block  of internal node \nf{n} is in the \nf{n.blocks[b]}'s left child or right child subblocks. From Definition  \ref{ordering} of $E(n,b)$ we know enqueue operations in a block are ordered by their process id and since the leaves of the tree are ordered by process id from left to right, thus operations from the left subblocks come before operations from the right subblocks in a block (See Figure \ref{figGet}). Furthermore the \nf{num\sub{enq-left}} field  in a block stores the number of \nf{enqueue()} operations from the blocks's subblocks in the left child of \nf{n}. So $i$th enqueue operation is propagated from the right child if \nf{i} is greater than \nf{b.num\sub{enq-left}}. otherwise we should search for the $i$th enqueue in the left child. By definition \ref{def::ops} and \ref{def::subblock} we need to search in subblocks of \nf{n.blocks[b]} from the range \texttt{n.left.blocks[n.blocks[i-1].end\textsubscript{left}+1..n.blocks[i].end\textsubscript{left}]} $\cup$ \texttt{n.right.blocks[n.blocks[i-1].end\textsubscript{right}+1..n.blocks[i].end\textsubscript{right}]}.

If the $i$th \nf{enqueue} of \nf{n.blocks[b]} is in the left child it would be $i$th enqueue in \texttt{n.left.blocks[n.blocks[i-1].end\textsubscript{left}+1..n.blocks[i].end\textsubscript{left}]} by Definition \ref{def::subblock}. Also we know there are $eb=n.blocks[b-1].sum_{enq-left}$ enqueues in the blocks before this range, so $E_i(n,b)$ is $E_{i+eb}(n.left)$ which is $E_{i^\prime}(n.left,b^\prime)$ for some $b^\prime$ and $i^\prime$. We can compute $b^\prime$ search for $i+eb$th enqueue in \tt{n.left} and $i^\prime$ is \tt{i+eb-n.left.blocks[}$b^\prime-1$\tt{].sum\sub{enq}}. The parameters in \ref{leftChildGet} are for searching $E_{i+eb}(n.left)$ in \nf{n.left.block} in the expected range of blocks, so this \nf{BSearch} returns the index of the subblock containing $E_i(n,b)$.

Else if the enqueue we are looking for is in the right child then there are \nf{n.blocks[b].num\sub{enq-left}} enqueues ahead of it in \nf{n.blocks[b]} but not in \texttt{n.right.blocks[n.blocks[i-1].end\textsubscript{right}+1..n.blocks[i].end\textsubscript{right}]}. So we need to search for \nf{i-n.blocks[b].num\sub{enq-left}+ n.blocks[b-1].sum\sub{enq-right}} (Line \ref{rightChildGet}). Other parameters are assigned similar for the left child. So in both cases the direct subblock containing $E_i(n,b)$ is computed in Lines \ref{leftChildGet} and \ref{rightChildGet}.

 Finally, \nf{n.child.GetENQ()} is invoked on the subblock containing $E_i(n,b)$ which returns $E_i(n,b)$ by the hypothesis of the induction.
\end{proof}

@@

\begin{lemma}[DSearch correctness] \label{dsearch}
Assume \nf{root.blocks[end].sum\sub{enq}}$\geq$\nf{e} and $E_e(root)$'s \nf{element} is the response to some \nf{Dequeue()} operation in \nf{root.blocks[end]}.  \nf{DSearch(e, end)} returns \nf{<b, i>} such that $E_i(root,b)= E_e(root)$.
\end{lemma}
\begin{proof}
It is trivial to see that the doubling search from \nf{root.blocks[end]} to \nf{root.blocks[0]} will find $E_e(root)$ eventually. Because \nf{root.blocks[].sum\sub{enq}} is an increasing value from 0 to some value greater than \nf{e}. So there is a \nf{b} that \nf{root.blocks[b].sum\sub{enq}}$>e$ but \nf{root.blocks[b-1].sum\sub{enq}}$<e$.

@@

@@

\begin{lemma}[Computing Response] \label{computeHead}
\nf{FindResponse(b,i)} returns \nf{R(D\sub{root,b,i}).element}.
\end{lemma}
\begin{proof}
First note that by Definition \ref{ordering} the linearization ordering  of operations will not change as new operations come so instead of talking about the linearization of operations before the $E_i(root, b)$ we talk about what if the whole operation in the linearization are applied on a queue.

$D_{root,b,i}$ is $D_{root,root.blocks[b-1].sum_{deq}+i}$ from the definition \ref{ordering} and \it{$sum_{enq}$}.  $D_{root,b,i}$ returns \nf{null} if \nf{root.blocks[b-1].\size+ root.blocks[b].num\sub{enq}- i <0} by Lemma \ref{nullReturn} (Line \ref{checkEmpty}). Otherwise if it is $d^\prime$th non-null dequeue in $L$ it returns $d^\prime$th enqueue by Observation \ref{responseToADeq} . By Lemma \ref{numberOfNND} there are \nf{root.blocks[b-1].sum\sub{enq} - root.blocks[b-1].\size} non-null dequeue operations before prefix for \nf{root.blocks[b-1]}. Note that the dequeues in \nf{root.blocks[b]} before the $i$th dequeue are non-null dequeues. So the response is $E_{i - root.blocks[b-1].size + root.blocks[b-1].sum\sub{deq}}(root)$ (Line \ref{computeE}). See figure \ref{computeResponseDetail}.

After computing \nf{e} we can find \nf{b,i} such that $E_i(root,b)=E_e(root)$ using \nf{DSearch} and then find its \nf{element} using \nf{GetEnq} (Line \ref{findAnswer}).
\end{proof}

\begin{figure}[hbt]  
  \center\includegraphics[width=2in]{pics/computeResponseDetail.png}\caption{The position of $E_i(root,b)$.}
\label{computeResponseDetail}
\end{figure}
